---
title: "replication"
author: "Zhirui Wang"
date: "August 5, 2016"
output: pdf_document
---

#table1
```{r}
Expected.Inflation <- read.csv("C:/Users/wang_/Desktop/Expected Inflation.csv")
CPIAUCSL <- read.csv("C:/Users/wang_/Desktop/CPIAUCSL.csv")
five_five_year <- 2*Expected.Inflation[,11]-Expected.Inflation[,6]
real <- CPIAUCSL[,2]/100
one_year <- Expected.Inflation[,2]
f_five_five_year <- five_five_year[-(1:12)]
d_five_five_year <- f_five_five_year-five_five_year[1:403]
x <- real[1:403]-one_year[1:403]
summary(lm(d_five_five_year[1:300]~x[1:300]))
summary(lm(d_five_five_year[1:84]~x[1:84]))
summary(lm(d_five_five_year[85:204]~x[85:204]))
summary(lm(d_five_five_year[205:300]~x[205:300]))
summary(lm(d_five_five_year[301:402]~x[301:402]))
```

#table2
```{r}
library(car)
library(lmtest)
CPIAUCSL2 <- read.csv("C:/Users/wang_/Desktop/CPIAUCSL (3).csv")
INDPRO <- read.csv("C:/Users/wang_/Desktop/INDPRO.csv")
pi <- CPIAUCSL2[,2,drop=F]
y <- INDPRO[,2,drop=F]
##US result 83-89
depen <- pi[432:515,]
indust <- y[1:84,]
indepen <- NA
indepen <- pi[431:514,,drop=F]
for (i in 1:47) {
  indepen <- cbind(indepen,pi[(431-i):(514-i),,drop=F])
}
(formula=depen ~ alpha+indepen[,1]*gamma+indepen[,2]*gamma*(1-gamma)+indepen[,3]*gamma*(1-gamma)^2
+indepen[,4]*gamma*(1-gamma)^3+indepen[,5]*gamma*(1-gamma)^4+indepen[,6]*gamma*(1-gamma)^5
+indepen[,7]*gamma*(1-gamma)^6+indepen[,8]*gamma*(1-gamma)^7+indepen[,9]*gamma*(1-gamma)^8
+indepen[,10]*gamma*(1-gamma)^9+indepen[,11]*gamma*(1-gamma)^10+indepen[,12]*gamma*(1-gamma)^11
+indepen[,13]*gamma*(1-gamma)^12+indepen[,14]*gamma*(1-gamma)^13+indepen[,15]*gamma*(1-gamma)^14
+indepen[,16]*gamma*(1-gamma)^15+indepen[,17]*gamma*(1-gamma)^16+indepen[,18]*gamma*(1-gamma)^17
+indepen[,19]*gamma*(1-gamma)^18+indepen[,20]*gamma*(1-gamma)^19+indepen[,21]*gamma*(1-gamma)^20
+indepen[,22]*gamma*(1-gamma)^21+indepen[,23]*gamma*(1-gamma)^22+indepen[,24]*gamma*(1-gamma)^23
+indepen[,25]*gamma*(1-gamma)^24+indepen[,26]*gamma*(1-gamma)^25+indepen[,27]*gamma*(1-gamma)^26
+indepen[,28]*gamma*(1-gamma)^27+indepen[,29]*gamma*(1-gamma)^28+indepen[,30]*gamma*(1-gamma)^29
+indepen[,31]*gamma*(1-gamma)^30+indepen[,32]*gamma*(1-gamma)^31+indepen[,33]*gamma*(1-gamma)^32
+indepen[,34]*gamma*(1-gamma)^33+indepen[,35]*gamma*(1-gamma)^34+indepen[,36]*gamma*(1-gamma)^35
+indepen[,37]*gamma*(1-gamma)^36+indepen[,38]*gamma*(1-gamma)^37+indepen[,39]*gamma*(1-gamma)^38
+indepen[,40]*gamma*(1-gamma)^39+indepen[,41]*gamma*(1-gamma)^40+indepen[,42]*gamma*(1-gamma)^41
+indepen[,43]*gamma*(1-gamma)^42+indepen[,44]*gamma*(1-gamma)^43+indepen[,45]*gamma*(1-gamma)^44
+indepen[,46]*gamma*(1-gamma)^45+indepen[,47]*gamma*(1-gamma)^46+indepen[,48]*gamma*(1-gamma)^47
+lamda*indust)
m1 <- nls(formula,start=list(alpha = 0, gamma = 0.246, lamda = 0))
coeftest(m1)

##US result 90-99
depen <- pi[516:635,]
indust <- y[85:204,]
indepen <- NA
indepen <- pi[515:634,,drop=F]
for (i in 1:47) {
  indepen <- cbind(indepen,pi[(515-i):(634-i),,drop=F])
}
m2 <- nls(formula,start=list(alpha = 0, gamma = 0.088, lamda = 0))
coeftest(m2)

##US result 00-07
depen <- pi[636:731,]
indust <- y[205:300,]
indepen <- NA
indepen <- pi[635:730,,drop=F]
for (i in 1:399) {
  indepen <- cbind(indepen,pi[(635-i):(730-i),,drop=F])
}
m3 <- nls(formula,start=list(alpha = 0, gamma = 0.05, lamda = 0))
coeftest(m3)

##US result 08-16
depen <- pi[732:833,]
indust <- y[301:402,]
indepen <- NA
indepen <- pi[731:832,,drop=F]
for (i in 1:47) {
  indepen <- cbind(indepen,pi[(731-i):(832-i),,drop=F])
}
m4 <- nls(formula,start=list(alpha = 0, gamma = 0, lamda = 0))
coeftest(m4)
```

#table3
```{r}
library(car)
library(lmtest)
CPI_headline <- read.csv("D:/Dropbox/16summer/Macroeconometrics/Paper/CPI_headline.csv")
Industrial.Production.Index <- read.csv("D:/Dropbox/16summer/Macroeconometrics/Paper/Industrial Production Index.csv")
a <- as.character(unique(Industrial.Production.Index[,1]))
table <- matrix(rep(NA,164),41,4)
rownames(table) <- a
colnames(table) <- c("Estimate", "Std. Error", "t value","Pr(>|t|)")
for(j in c(1:41)){
  b <- a[j]
  pi <- CPI_headline[CPI_headline[,1]==b,7,drop=F]
  pi1 <- data.frame(rep(NA,270))
  for (i in 1:270) {
    pi1[i,1] <- (pi[i+1,1,drop=F]-pi[i,1,drop=F])/pi[i,1,drop=F]
  }
  pi<- ((1+pi1[,1,drop=F])^4-1)*100
  y <- Industrial.Production.Index[Industrial.Production.Index[,1]==b,7,drop=F]
  y1 <- rep(NA,216)
  for (i in 1:216) {
    y1[i] <- (y[i+1,1]-y[i,1])/y[i,1]
  }
  y <- ((1+y1)^4-1)*100
  depen <- pi[25:240,1]
  indust <- y[1:216]
  indepen <- NA
  indepen <- pi[24:239,1,drop=F]
  for (i in 1:23) {
    indepen <- cbind(indepen,pi[(24-i):(239-i),1,drop=F])
  }
  (formula=depen ~ alpha+indepen[,1]*gamma+indepen[,2]*gamma*(1-gamma)+indepen[,3]*gamma*(1-gamma)^2
  +indepen[,4]*gamma*(1-gamma)^3+indepen[,5]*gamma*(1-gamma)^4+indepen[,6]*gamma*(1-gamma)^5
  +indepen[,7]*gamma*(1-gamma)^6+indepen[,8]*gamma*(1-gamma)^7+indepen[,9]*gamma*(1-gamma)^8
  +indepen[,10]*gamma*(1-gamma)^9+indepen[,11]*gamma*(1-gamma)^10+indepen[,12]*gamma*(1-gamma)^11
  +indepen[,13]*gamma*(1-gamma)^12+indepen[,14]*gamma*(1-gamma)^13+indepen[,15]*gamma*(1-gamma)^14
  +indepen[,16]*gamma*(1-gamma)^15+indepen[,17]*gamma*(1-gamma)^16+indepen[,18]*gamma*(1-gamma)^17
  +indepen[,19]*gamma*(1-gamma)^18+indepen[,20]*gamma*(1-gamma)^19+indepen[,21]*gamma*(1-gamma)^20
  +indepen[,22]*gamma*(1-gamma)^21+indepen[,23]*gamma*(1-gamma)^22+indepen[,24]*gamma*(1-gamma)^23
  +lamda*indust)
  m <- nls(formula,start=list(alpha = 0, gamma = 0.2, lamda = 0),control = list(maxiter=500))
  table[j,] <- coeftest(m)[2,]
}
table[order(table[,1],decreasing = TRUE),]

```

#table4
```{r}
library(car)
library(lmtest)
CPI_core <- read.csv("D:/Dropbox/16summer/Macroeconometrics/Paper/CPI_core.csv")
Industrial.Production.Index <- read.csv("D:/Dropbox/16summer/Macroeconometrics/Paper/Industrial Production Index.csv")
a <- intersect(unique(CPI_core[,1]),unique(Industrial.Production.Index[,1]))
table <- matrix(rep(NA,1152),38,4)
rownames(table) <- a
colnames(table) <- c("Estimate", "Std. Error", "t value","Pr(>|t|)")
for(j in c(1:38)){
  b <- a[j]
  pi <- CPI_core[CPI_core[,1]==b,7,drop=F]
  pi1 <- data.frame(rep(NA,270))
  for (i in 1:270) {
    pi1[i,1] <- (pi[i+1,1,drop=F]-pi[i,1,drop=F])/pi[i,1,drop=F]
  }
  pi<- ((1+pi1[,1,drop=F])^4-1)*100
  y <- Industrial.Production.Index[Industrial.Production.Index[,1]==b,7,drop=F]
  y1 <- rep(NA,216)
  for (i in 1:216) {
    y1[i] <- (y[i+1,1]-y[i,1])/y[i,1]
  }
  y <- ((1+y1)^4-1)*100
  depen <- pi[25:240,1]
  indust <- y[1:216]
  indepen <- NA
  indepen <- pi[24:239,1,drop=F]
  for (i in 1:23) {
    indepen <- cbind(indepen,pi[(24-i):(239-i),1,drop=F])
  }
  (formula=depen ~ alpha+indepen[,1]*gamma+indepen[,2]*gamma*(1-gamma)+indepen[,3]*gamma*(1-gamma)^2
  +indepen[,4]*gamma*(1-gamma)^3+indepen[,5]*gamma*(1-gamma)^4+indepen[,6]*gamma*(1-gamma)^5
  +indepen[,7]*gamma*(1-gamma)^6+indepen[,8]*gamma*(1-gamma)^7+indepen[,9]*gamma*(1-gamma)^8
  +indepen[,10]*gamma*(1-gamma)^9+indepen[,11]*gamma*(1-gamma)^10+indepen[,12]*gamma*(1-gamma)^11
  +indepen[,13]*gamma*(1-gamma)^12+indepen[,14]*gamma*(1-gamma)^13+indepen[,15]*gamma*(1-gamma)^14
  +indepen[,16]*gamma*(1-gamma)^15+indepen[,17]*gamma*(1-gamma)^16+indepen[,18]*gamma*(1-gamma)^17
  +indepen[,19]*gamma*(1-gamma)^18+indepen[,20]*gamma*(1-gamma)^19+indepen[,21]*gamma*(1-gamma)^20
  +indepen[,22]*gamma*(1-gamma)^21+indepen[,23]*gamma*(1-gamma)^22+indepen[,24]*gamma*(1-gamma)^23
  +lamda*indust)
  m <- nls(formula,start=list(alpha = 0, gamma = 0.5, lamda = 0),control = list(maxiter=5000))
  table[j,] <- coeftest(m)[2,]
}
table[order(table[,1],decreasing = TRUE),]

```

#Ideas for extention
My extension will mainly focus on the update of data period. The paper use data from 1983-2007 in table 1 and 2, while I add 2008-2016 period into the results, to estimate the inflation expectation in the post-recession period. Also in the cross-country comparison, the authors use data from 1996-2013, while I can use data from 1996-2016 to make the estimate more power. In the moving-window estimates, I will also add more recent data into the graph.I expect to see a more anchored result of recent data than the original paper because the inflation is more targeted by the central bank of most countries recently. And in the paper I will discuss more about it.
